On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement

### 2023-10-15 manuscript/manuscript.tex
manuscript: title, keywords, and final touches main text
manuscript: add data and code availability section

	\title{Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement}

@@

	\begin{keyword}
		TODO
	\end{keyword}

@@

%\listoftodos[TODOs]
\tableofcontents

@@

This project is also developed as open-source. \url{https://github.com/PyPSA/247-cfe}

The data and code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.

The online dashboard with the results for this study is available at \url{dashboard}.

>>>>

	\title{On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement}

@@

	\begin{keyword}
		24/7 carbon-free electricity, 
		Clean electricity procurement, 
		Energy modelling, 
		Renewable energy
	\end{keyword}

@@

\tableofcontents

@@

The simulations were carried out with PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.

All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub: \href{https://github.com/Irieo/247-procurement-paper}{github.com/Irieo/247-procurement-paper}.

We publish an online dashboard with results for the entire scenario space alongside the paper \href{}{DASHBOARD}.
